Computational musicology, ????, Profit

### 2016-07-24 paper.tex
Fix Minsky references.

Marvin Minksy recognises this problem in an essay called `Music, Mind, and Meaning'. He suggests that computational
musicologists ``would like to study Mozart's music the way scientists analyze the spectrum of a distant star``, but that music
is not the kind of object that can be studied ``uninfluenced by custom or constraint of commerce"\cite{Music, Mind and Meaning}.
I deliberately refer to Minsky's work as an essay and not as a paper. It does not conform to the conventions of a scientific
or mathematical paper. He uses the first person. He speculates. He draws connections that he cannot mathematically formalise.
He makes painstaking reference to the details of a specific artistic work (Beethoven's Fifth). He states no theorems.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Online Library of Babel} Basile, Jonathan: \verb|libraryofbabel.info|, \url{https://libraryofbabel.info}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
\bibitem{The Library of Babel} Borges, Jorge Luis: `The Library of Babel' in The Garden of Forking Paths, \textit{Editorial Sur}, 1941.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
\bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda: TODO. 
\bibitem{Three Paradigms} Eden, Amnon, Three Paradigms of Computer Science, \textit{Minds and Machines}, volume 17, number 2, July, 2007.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Series A}, volume 25, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{The Digital Computer as a Musical Instrument} Mathews, M. V., \textit{Science}, 1963. TODO.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{Music, Mind and Meaning} Minsky, Marvin. 1981.
\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
\bibitem{Two Cultures} Snow, Charles Percy: The Two Cultures and the Scientific Revolution, \textit{Cambridge University Press}, 1959.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.

>>>>

Marvin Minksy recognises this problem in an essay called `Music, Mind, and Meaning'. He suggests that computational
musicologists ``would like to study Mozart's music the way scientists analyze the spectrum of a distant star", but that music
is not the kind of object that can be studied ``uninfluenced by custom or constraint of commerce"\cite{Music Mind and Meaning}.
I deliberately refer to Minsky's work as an essay and not as a paper. It does not conform to the conventions of a scientific
or mathematical paper. He uses the first person. He speculates. He draws connections that he cannot mathematically formalise.
He makes painstaking reference to the details of a specific artistic work (Beethoven's Fifth). He states no theorems.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Online Library of Babel} Basile, Jonathan: \verb|libraryofbabel.info|, \url{https://libraryofbabel.info}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
\bibitem{The Library of Babel} Borges, Jorge Luis: `The Library of Babel' in The Garden of Forking Paths, \textit{Editorial Sur}, 1941.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
\bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda: TODO. 
\bibitem{Three Paradigms} Eden, Amnon, Three Paradigms of Computer Science, \textit{Minds and Machines}, volume 17, number 2, July, 2007.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Series A}, volume 25, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{The Digital Computer as a Musical Instrument} Mathews, M. V., \textit{Science}, 1963. TODO.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{Music Mind and Meaning} Minsky, Marvin. 1981.
\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
\bibitem{Two Cultures} Snow, Charles Percy: The Two Cultures and the Scientific Revolution, \textit{Cambridge University Press}, 1959.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.
